---
title: "Notes + Test Code for County Map"
author: "John Bowman"
date: "3/9/2017"
output: html_document
---

Library
```{r Library}
library(dplyr)
```


#Leaflet Test
##Data
Sourced from: http://eric.clst.org/wupl/Stuff/gz_2010_us_050_00_5m.json
              http://eric.clst.org/wupl/Stuff/gz_2010_us_040_00_5m.json
Need to cite US Census Beauro, see (http://eric.clst.org/Stuff/USGeoJSON) for more info

All actual data sourced from NIOSH, need to find urls, etc. (add in dates / redownload for final)
```{r Data leaflet, cache = TRUE}
uscounties <- rgdal::readOGR("data/counties_5m.json", "OGRGeoJSON")
usstates   <- rgdal::readOGR("data/state_5m.json", "OGRGeoJSON")
```

#Data merging: rapidProgression
We will use rapidProgression_clean for these plots (only df that has county info built in)
##Data
```{r Data rapidProgression}
rapidProg_raw <- read.csv("~/CWP-trends/data/rapidProgression_clean.csv")

rapidProg_raw$X <- NULL
```

##Join State and Country DFs
```{r join df}
uscounties$REGION <- NA
usstates$REGION   <- NA

states <- as.data.frame(usstates$NAME)
states$STATE <- (usstates$STATE)

df_counties <- as.data.frame(uscounties)
df_join     <- dplyr::left_join(df_counties, states, by = "STATE")
```

##Assign Rergions to states/counties

###Northern Appalachia
```{r Northern Appalachia}
df_join <- within(df_join, REGION[`usstates$NAME` %in% c( 'Maryland'
                                                        , 'Pennsylvania'
                                                        , 'Ohio'
                                                        )
                                 ] <- 'Northern Appalachia')

df_join <- within(df_join, REGION[`usstates$NAME` == 'West Virginia' & NAME %in% c( "Barbour"
                                                                                  , "Brooke"
                                                                                  , "Clay"
                                                                                  , "Grant"
                                                                                  , "Greenbrier"
                                                                                  , "Harrison"
                                                                                  , "Lincoln"
                                                                                  , "Marion"
                                                                                  , "Marshall"
                                                                                  , "Monongalia"
                                                                                  , "Preston"
                                                                                  , "Raleigh"
                                                                                  , "Randolph"
                                                                                  , "Tucker"
                                                                                  , "Upshur"
                                                                                  , "Webster"
                                                                                  )
                                  ] <- 'Northern Appalachia'
                  )
```

###Mid-West
```{r Mid-West}
df_join <- within(df_join, REGION[`usstates$NAME` %in% c( 'Illinois'
                                                        , 'Indiana'
                                                        )
                                 ] <- 'Mid-West')

df_join <- within(df_join, REGION[`usstates$NAME` == 'Kentucky' & NAME %in% c( "Hopkins"
                                                                             , "Union"
                                                                             , "Webster"
                                                                             )
                                  ] <- 'Mid-West')
```

###Central Appalachia
```{r Central Appalachia}
df_join <- within(df_join, REGION[`usstates$NAME` %in% c( 'Virginia'
                                                        , 'Tennessee'
                                                        )
                                 ] <- 'Central Appalachia')

df_join <- within(df_join, REGION[`usstates$NAME` == 'Kentucky' & NAME %in% c( "Bell"
                                                                             , "Boyd"
                                                                             , "Breathitt"
                                                                             , "Christian"
                                                                             , "Clay"
                                                                             , "Daviess"
                                                                             , "Estill"
                                                                             , "Floyd"
                                                                             , "Harlan"
                                                                             , "Henderson"
                                                                             , "Jackson"
                                                                             , "Johnson"
                                                                             , "Knott"
                                                                             , "Knox"
                                                                             , "Laurel"
                                                                             , "Lawrence"
                                                                             , "Leslie"
                                                                             , "Letcher"
                                                                             , "Martin"
                                                                             , "Mclean"
                                                                             , "Muhlenberg"
                                                                             , "Perry"
                                                                             , "Pike"
                                                                             , "Whitley"
                                                                             , "Wolfe"
                                                                             )
                                  ] <- 'Central Appalachia')

df_join <- within(df_join, REGION[`usstates$NAME` == 'West Virginia' & NAME %in% c( "Boone"
                                                                             , "Fayette"
                                                                             , "Kanawha"
                                                                             , "Logan"
                                                                             , "McDowell"
                                                                             , "Mingo"
                                                                             , "Nicholas"
                                                                             , "Wayne"
                                                                             , "Wyoming"
                                                                           
                                                                             )
                                  ] <- 'Central Appalachia')
```

###Southern Appalachia
```{r Southern Appalachia}
df_join <- within(df_join, REGION[`usstates$NAME` %in% c( 'Alabama'
                                                        , 'Arkansas'
                                                        , 'Louisiana'
                                                        )
                                  ] <- 'Southern Appalachia')
```

###West
```{r West}
df_join <- within(df_join, REGION[`usstates$NAME` %in% c( 'Arizona'
                                                        , 'Colorado'
                                                        , 'Montana'
                                                        , 'New Mexico'
                                                        , 'North Dakota'
                                                        , 'Oklahoma'
                                                        , 'Texas'
                                                        , 'Utah'
                                                        , 'Wyoming'
                                                        , 'Washington'
                                                        )
                                  ] <- 'West')
```

#Add in DISEASE column to rapidProg_raw with PMF or CWP labels
PMF Stages = A, B, C
CWP = 1 or greater

```{r}
rapidProg <- rapidProg_raw
rapidProg$DISEASE <- NA

rapidProg <- within(rapidProg, DISEASE[FINAL_CATEGORY %in% c( 1
                                                            , 10
                                                            , 11
                                                            , 12
                                                            , 2
                                                            , 21
                                                            , 22
                                                            , 23
                                                            , 32
                                                            , 33
                                                            ) & FINAL_STAGE == 'O'
                                       ] <- 'CWP')

rapidProg <- within(rapidProg, DISEASE[FINAL_STAGE %in% c( "A"
                                                         , "B"
                                                         , "C"
                                                         )
                                       ] <- 'PMF')
```


Number of Pmf and Cwp cases from rapid prog and final join
```{r}
merge <- rapidProg %>%
          group_by(XRAY_YEAR, REGION, DISEASE) %>%
          summarise(n = n())

merge <- merge[!is.na(merge$DISEASE),]

final_join <- left_join(df_join, merge, by = "REGION")
final_join <- final_join[!is.na(final_join$REGION),]
```

##Add in needed values to plugon county object
```{r leaflet}
toMerge <- final_join[,-c(2:6, 8)]
```

#Save counties polygon object for loading into server.ui
```{r Save Data}
uscounties <- rgdal::readOGR("data/counties_5m.json", "OGRGeoJSON")
usstates   <- rgdal::readOGR("data/state_5m.json", "OGRGeoJSON")

save( toMerge
    , uscounties
    , usstates
    , file = "data/serverData.RData")
```